This is the title [Article v\versionnumber]

### 2022-08-28 manuscript/manuscript.tex
Paragraph about Streptavidin, intro sentence for GIST usage

\section{Running GIST}
%\subsection{Running the GIST analysis}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}

@@

\section{Tutorial}
Here, we aim to guide the reader through a GIST analysis of the streptavidin-biotin complex. The goal is to
\begin{enumerate}
	\item compute the binding free energy of the complex from the individual energy contributions combined with the contribution of hydration computed using GIST.
	\item visualize local contributions to $\dgsolv$ in the streptavidin binding pocket as well as around biotin.
\end{enumerate}
\todo{include: learn how to setup ad run a gist calculation}

\subsection{Streptavidin/Biotin}
\subsection{Tutorial data}
We will use the 1STP crystal structure to start our calculations.
For the sake of simplicity, you can download prepared and solvated Amber topologies and structures based on 1STP by running
\begin{lstlisting}
git clone git@github.com:liedllab/gist-tutorial.git
\end{lstlisting}
This will download the tutorial files (including both the manuscript and the examples in the \software{code} folder).
\subsection{System Preparation and Equilibration}
If you want to skip this section, run 
\begin{lstlisting}
make equilibration-targets
\end{lstlisting}
in the code folder. This assumes that you have Python and Amber set up properly and that \software{pmemd.cuda} is in the PATH.

>>>>

\section{Running GIST}
%\subsection{Running the GIST analysis}
To run a gist analyis, the following is required:
\begin{itemize}
	\item A running installation of \software{cpptraj}.
	\item A topology of the molecule of interest in a solvent box.
	\item An MD trajectory of that system.
\end{itemize}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}

@@

\section{Tutorial}
Here, we aim to guide the reader through a GIST analysis of the streptavidin-biotin complex.
In the process, the reader will learn how to set up and run a GIST calculation.
During the tutorial, we will
\begin{enumerate}
	\item compute the binding free energy of the complex from the individual energy contributions combined with the contribution of hydration computed using GIST.
	\item visualize local contributions to $\dgsolv$ in the streptavidin binding pocket as well as around biotin.
\end{enumerate}

\subsection{Streptavidin/Biotin}
The streptavidin-biotin complex is one of the strongest known non-covalent interactions involving a small molecule.
Therefore, the combination of streptavidin and biotin is used routinely in biotechnology, and the interaction between them has been investigated in detail \todo{CITE}\cite{}.

In nature, streptavidin occurs as a tetramer, and binds biotin with a binding constant of \todo{???}.
Here, we will investigate the binding of biotin to a streptavidin monomer for simplicity.
This interaction has been reported to have a binding constant of \todo{???}.

\subsection{Tutorial data}
We will use the 1STP crystal structure to start our calculations.
For the sake of simplicity, you can download prepared and solvated Amber topologies and structures based on 1STP by running
\begin{lstlisting}
git clone git@github.com:liedllab/gist-tutorial.git
\end{lstlisting}
This will download the tutorial files (including both the manuscript and the examples in the \software{code} folder).
\subsection{System Preparation and Equilibration}
If you want to skip this section, run 
\begin{lstlisting}
make equilibration-targets
\end{lstlisting}
in the code folder. This assumes that you have Python and Amber set up properly and that \software{pmemd.cuda} is in the PATH.
